Alternate {\ttlit ACM} SIG Proceedings Paper in LaTeX Format

### 2017-12-02 paper.tex

>>>>

Increased interactions of the new interfaces and system architectures discussed
above further complicate the duties of the storage system. As developers start
to push application-specific optimizations into the storage system, the storage
system must continue to provide the semantics and guarantees that users have
come to expect. Code-hardened subsystems that use QoS, scheduling, and load
balancing must now account for this new dimension. This problem is especially
relevant for data-intensive HPC applications that need these internal
optimizations, such as scheduling and locality, to retrieve data from and store
data on heterogeneous hardware.

As with the other research directions, operational policies reach beyond just
HPC. Providing performance guarantees for all resources, not just storage, is
important for *aaS architectures that are shared among users, so lessons can be
gleaned from cloud research about isolation and scheduling, such as Mesos and
Kubernetes. Furthermore, the cloud community has done a good job addressing
heterogeneity when using these techniques behind user-facing APIs without
jeopardizing the semantics.
